---
title: "Result File"
author: "An Tran"
date: "2024-01-26"
output: html_document
---
***
<style>

body {
  font-family: "Georgia";
  text-align: justify;
}

p {
  font-family: "Georgia";
  text-indent: 30px;
  color: black;
  font-style: normal;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
```

# Import library
```{r}
#install.packages(quantmod)
#install.packages(forecast)
#install.packages(TTR)
#install.packages(tseries)
#install.packages(ggplot2)
#install.packages(tidyquant)
library(quantmod)
library(forecast)
library(TTR)
library(tseries)
library(ggplot2)
library(tidyquant)
library(lmtest)
library(dplyr)
library(stats)
```
# Import Stock Data

```{r}
# Load historical stock price data
symbol <- "MARA" 
start_date <- "2012-05-05"
end_date <- "2023-12-31"

# Fetch historical stock price data using tidyquant
stock_data <- tq_get(symbol, from = start_date, to = end_date, daily.return = "Cl")

# Handle missing values or outliers
stock_data <- stock_data %>%
  na.omit()

# Define date range
start_date <- as.Date("2021-01-01")
end_date <- as.Date("2023-06-30")

# Select rows within the date range and include all columns
selected_rows <- stock_data %>%
  filter(as.Date(date) >= start_date & as.Date(date) <= end_date)

data <- selected_rows %>%
  tq_transmute(select = adjusted,
               mutate_fun = to.daily,
               indexAt = "endof")

# Print the first few rows of data
print(head(data,100))
print(head(stock_data,1))
```

# Transform the data by using logarithm return

```{r}
data$adjusted=as.numeric(gsub(',', '', data$adjusted))

data <- data.frame(data$date, data$adjusted)
df <- na.omit(data)
df$date <- df$data.date
df$price <- df$data.adjusted
df$return <- c(0, diff(log(df$price)))

```
# Import data from Jul-Aug 2023 (using for compare only)

```{r} 
# Define date range
new_start_date <- as.Date("2023-07-01")
new_end_date <- as.Date("2023-08-14")

# Select rows within the date range and include all columns
new_selected_rows <- stock_data %>%
  filter(as.Date(date) >= new_start_date & as.Date(date) <= new_end_date)

#
new_data <- new_selected_rows %>%
  tq_transmute(select = adjusted,
               mutate_fun = to.daily,
               indexAt = "endof")

# Print the first few rows of data
print(head(new_data,100))
print(head(stock_data,1))

new_data$adjusted=as.numeric(gsub(',', '', new_data$adjusted))

new_data <- data.frame(new_data$date, new_data$adjusted)
new_df <- na.omit(new_data)
new_df$date <- new_df$new_data.date
new_df$price <- new_df$new_data.adjusted
new_df$return <- c(0, diff(log(new_df$price)))
```

# Explore and Visualize Data

```{r}
# Plot the time series data (using adjusted price to calculate from now on)
plot(df$date, df$price, type = "l", col = "black", lwd = 2, xlab = "Date", ylab = "USD", main = "Stock Price of Marathon Digital Holdings, Inc.")

#Log return
plot(df$date, df$return, type = "l", col = "black", lwd = 2, xlab = "Date", ylab = "Return", main = "Log Return of Marathon Digital Holdings, Inc.")
```

# Check series is stationary or not

```{r}
adf.test(df$return)
```
# ARIMA
```{r}
model <- auto.arima(df$return)
summary(model)
```

# ACF and PACF

```{r}
pacf((df$return), lag=12, main = "PACF for Return, Marathon Digital Holdings, Inc.")
acf((df$return),lag=12, main = "ACF for Return, Marathon Digital Holdings, Inc.")
```

#AIC BIC

```{r}
AIC(model)
BIC(model)
```

# Check residuals

```{r}
residuals <- resid(model)
# Residual plot
plot(residuals, main = "Residuals Plot")

# Ljung-Box test
ljung_box_test <- Box.test(residuals, lag = 20, type = "Ljung-Box")
print(ljung_box_test)
```

# Dynamic Forecast

```{r}
ar23 <- arima(df$return, order = c(2, 0, 3))
dynamic_fc <- predict(ar23, n.ahead = 30)
head(dynamic_fc)
```

# Static Forecast

```{r}
static_fc = ar23$coef[3] + ar23$coef[1] * df$return[1:626] + ar23$coef[2] * df$return[1:626]

# Use the last value in the static forecast as the starting point for the next 30 days
last_value <- tail(static_fc, 1)
extended_static_fc <- numeric(30)

# Forecast the next 30 days using the last value from the static forecast
for (i in 1:30) {
  extended_static_fc[i] <- ar23$coef[3] + ar23$coef[1] * last_value + ar23$coef[2] * last_value
  last_value <- extended_static_fc[i]
}

# Convert 'extended_static_fc' into a time series object
extended_static_fc_ts <- ts(extended_static_fc, start = end(df$date), frequency = 1)

# Print the extended static forecast for the next 30 days as a time series
cat("\nExtended Static Forecast (Next 30 days):\n")
print(extended_static_fc_ts)
head(extended_static_fc_ts)
```

# Combine data into 1 data frame

```{r}
# Create a new data frame by combining the original data frame with the time series
combined_df <- cbind(new_df, TimeSeries = dynamic_fc, TimeSeries = extended_static_fc_ts)

# Print the first few rows of the combined data frame
#print(head(combined_df))

# Print specific columns from the combined data frame
#print(combined_df[, c("date", "return", "TimeSeries.pred", "TimeSeries")])
print(combined_df %>%
      select('Date' = date, 'Actual value' = return, `Dynamic Forecast` = TimeSeries.pred, `Static Forecast` = TimeSeries))
```

# Plot dynamic forecast vs actual value

```{r}
par(lwd = 1, cex.axis = 1)

# Create a line plot with reduced x-axis labels
plot(combined_df$date, combined_df$return, type = "l", xlab = "", ylab = "", main = "Actual and Forecast for Return, Marathon Holdings Inc.", xaxt = "n")

# Add the blue line
lines(combined_df$date, combined_df$TimeSeries.pred, col = "blue")

# Customize the x-axis with fewer labels
axis(1, at = seq(from = min(combined_df$date), to = max(combined_df$date), length.out = 6), labels = seq(from = min(combined_df$date), to = max(combined_df$date), length.out = 6))

# Customize the y-axis with fewer labels
axis(1, at = seq(from = min(combined_df$return), to = max(combined_df$return), length.out = 6), labels = seq(from = min(combined_df$return), to = max(combined_df$return), length.out = 6))

# Add a legend
legend("topright", legend = c("Actual", "Dynamic"), col = c("black", "blue"), lty=1)
```

# MSE, ME, MAE for Dynamic Forecast

```{r}
predicted_values <- dynamic_fc$pred

# Assuming 'df$return' is your observed time series
observed_values <- df$return

# Ensure both vectors have the same length
min_length <- min(length(observed_values), length(predicted_values))
observed_values <- observed_values[1:min_length]
predicted_values <- predicted_values[1:min_length]

# Calculate Mean Squared Error (MSE)
mse <- mean((observed_values - predicted_values)^2)
cat("Dynamic Forecast Mean Squared Error (MSE):", mse, "\n")

# Calculate Mean Absolute Error (MAE)
mae <- mean(abs(observed_values - predicted_values))
cat("Dynamic Forecast Mean Absolute Error (MAE):", mae, "\n")

# Calculate Mean Error (ME)
me <- mean(observed_values - predicted_values)
cat("Dynamic Forecast Mean Error (ME):", me, "\n")
```